A Large-Scale Study of Polymorphism in R

### 2019-04-06 paper/main.tex
merge

In R, all arguments are passed as promises, and unused arguments will be unevaluated. 
Our recording mechanism captures the order in which arguments are passed, can figure out which arguments were {\it not} provided (recording them as {\it missing} if the missing argument has no default value), and does {\it not} force unforced promises, recording unforced promises as {\it unevaled}.
In R, trying to use missing values results in an error and thus an exception, triggering our recording phase: arguments which cause errors in this way are recorded as {\it error}.
For practical reasons, we do not record the contents of environments:
These can be used as hash tables, may be large, and are quite likely different from one another.

@@

More generally, there is an existing literature on analyzing usage patterns of language features.  
For instance, the dynamic features of Smalltalk were analyzed in some work~\cite{callau2011howdevelopers}, which aimed to see how often the highly dynamic capabilities of Smalltalk were used and in which kinds of projects.

>>>>

In R, all arguments are passed as promises, and unused arguments will remain unevaluated promises, which we record as {\it unevaled}. 
Our recording mechanism captures the order in which arguments are passed, can figure out which arguments were {\it not} provided (recording them as {\it missing} if the missing argument has no default value), and does {\it not} force unforced promises.
In R, trying to use missing values results in an error and thus an exception, triggering our recording phase: arguments which cause errors in this way are recorded as {\it error}.
For practical reasons, we do not record the contents of environments:
These can be used as hash tables, may be large, and are quite likely different from one another.

@@

More generally, there is an existing literature on analyzing usage patterns of language features.  
For instance, the dynamic features of Smalltalk were analyzed in some work~\cite{callau2011howdevelopers}, which aimed to see how often the highly dynamic capabilities of Smalltalk were used and in which kinds of projects.
Other work~\cite{pldi10a} explores how the dynamic features of JavaScript are used.
An interesting finding of theirs is that
